Verifying Spatial Properties of Array Computations

### 2017-04-13 oopsla17/appendix.tex
moving the model into the main text and adapting
corpus data'

@@

>>>>

\begin{table}
\centering
\footnotesize
\begin{tabular}{lS[table-format=4]S[table-format=4]S[table-format=4]S[table-format=4]S[table-format=4]S[table-format=4]}
\hline
  & \multicolumn{2}{c}{Number of files}
  & \multicolumn{2}{c}{Lines of physical code}
  & \multicolumn{2}{c}{Lines of raw code} \\
%%
  Package   & {Total} & {Parsed}& {\hspace{2em}Total} & {Parsed} & {\hspace{2em}Total} & {Parsed}  \\ % braces prevent headers from being formatted as numbers
  \hline
%%%
  ARPACK-NG & \SSArpackFiles & \SSArpackFilesParsed & \SSArpackLoC &
\SSArpackLoCParsed & \SSArpackLoCRaw & \SSArpackLoCParsedRaw \\
%%%
  BLAS & \SSBlasFiles & \SSBlasFilesParsed &
\SSBlasLoC & \SSBlasLoCParsed & \SSBlasLoCRaw & \SSBlasLoCParsedRaw \\
%%%
  Cliffs & \SSCliffsFiles & \SSCliffsFilesParsed & \SSCliffsLoC &
\SSCliffsLoCParsed & \SSCliffsLoCRaw & \SSCliffsLoCParsedRaw \\
%%%
  CP & \SSCPFiles & \SSCPFilesParsed & \SSCPLoC & \SSCPLoCParsed &
\SSCPLoCRaw & \SSCPLoCParsedRaw \\
%%%
  E3MG & \SSEThreeMEFiles & \SSEThreeMEFilesParsed & \SSEThreeMELoC &
\SSEThreeMELoCParsed & \SSEThreeMELoCRaw & \SSEThreeMELoCParsedRaw \\
%%%
  GEOS-Chem &
\SSgeosChemFiles & \SSgeosChemFilesParsed & \SSgeosChemLoC &
\SSgeosChemLoCParsed & \SSgeosChemLoCRaw & \SSgeosChemLoCParsedRaw \\
%%%
  Hybrid4 & \SShybridFiles & \SShybridFilesParsed & \SShybridLoC &
\SShybridLoCParsed & \SShybridLoCRaw & \SShybridLoCParsedRaw \\
%%%
  Navier & \SSnavierFiles & \SSnavierFilesParsed & \SSnavierLoC &
\SSnavierLoCParsed & \SSnavierLoCRaw & \SSnavierLoCParsedRaw \\
%%
  Specfem3D & \SSspecfemFiles & \SSspecfemFilesParsed & \SSspecfemLoC &
\SSspecfemLoCParsed & \SSspecfemLoCRaw & \SSspecfemLoCParsedRaw \\
%%
  UM &
\SSumFiles & \SSumFilesParsed & \SSumLoC & \SSumLoCParsed &
\SSumLoCRaw & \SSumLoCParsedRaw \\ \hline
%%% TOTAL
  \textbf{Total} & \SSFiles &
\SSFilesParsed & \SSLoC & \SSLoCParsed & \SSLoCRaw & \SSLoCParsedRaw
\end{tabular}
\caption{Summary of software packages used for
  evaluation\label{tab:corpus}}
\vspace{-1em}
\end{table}

@@

\section{Proofs and extended definitions for the model}
\label{sec:proofs}

\input{proofs}
